other functionalities

### 2025-07-17 inst/gitbook/05_other-functionalities.Rmd

>>>>

To play around with different sampling strategies, but if your estimations take a lot of time, you can save your estimations as a `"multi.ace"` object that you can then recycle and reuse very easily:

```{r}
## Saving the estimation without getting any estimate (raw):
raw_estimates <- multi.ace(data, my_tree, output = "multi.ace`")

## Sampling from the raw_estimates
sampled_estimates <- multi.ace(raw_estimates, sample = 100)
```
